X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt}

### 2013-09-09 hedpc_natphys.tex
Zhentian's and Christian's review
- abstract: "present" edge-on illumination
- added very short description of the dark field
    "In addition to phase sensitivity, these techniques provide a dark-field
    contrast, also called scatter contrast or visibility-reduction contrast,
    that is proportional to the scatter strength of details in the
    sample\cite{Pfeiffer2008}."
- exposure time: 24 phase steps "per line" (both in methods and in caption)
- fixed Microworks spelling
- a more efficient detector can also shorten the exposure

- added bibtex Makefile target
- removed useless binaries

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    suggest edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match beam
    divergence and allow large field of views on a short and efficient
    setup.
\end{abstract}
\maketitle

@@

The attenuation and phase shift properties are described by the complex index of refraction
$n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$.
The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the
attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi
\beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object
of thickness $d$ can be described by the line integral $L_\mu = \int_0^d
\mu(\mathbf{r},\lambda) \d l$. Similarly, the real part
$\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by
$\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi =
\int_0^d \phi(\mathbf{r}) \d l$.

@@

In the past, a lot of effort has been invested into the development of
techniques which are sensitive to the phase shift. Since most of the
available phase contrast techniques rely on interference and thus typically
on optical hardware (e.g. crystals, gratings), they vary a lot in terms of
sensitivity, practical applicability or achievable resolution. The vast
majority of the methods, including crystal analyzer based
\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Techniques which are compatible with
an X-ray beam of low temporal coherence (broad bandwidth) are the inline
phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded
apertures \cite{Munro2012}.

Talbot interferometry has been demonstrated using a synchrotron source at
$\SI{82}{\kilo\electronvolt}$ \cite{Willner2013} and
$\SI{123}{\kilo\electronvolt}$\cite{Ruiz2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied at $\SI{60}{\kilo\electronvolt}$ mean energy \cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require energies between $100$ and
$\SI{150}{\kilo\electronvolt}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

Here, we introduce a method for phase-contrast imaging which is
compatible with the entire diagnostic energy range of X-rays. Moreover, the
method is fully compatible with compact imaging arrangements based on
conventional X-ray tubes. The method is based on Talbot-Lau interferometry
\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
arrangement. 
The challenge which limited the progress towards higher energies was mainly
related to the manufacturing of gratings with high aspect ratios. The aspect
ratio, given by
\begin{equation}
    \text{AR} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the grating structure
height, is normally limited by the lithographic process, as grating
structures tend to collapse or to deform (e.g. through capillary forces) if
the aspect ratio is too high. For a given setup distance these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{AR}
\propto E^{7/2}$\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating of around $\textnormal{AR}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently attenuated by the gratings, which requires even higher aspect ratios.
Maximum achievable aspect ratios of current grating fabrication techniques
\cite{David2007,Kenntner2010} are approximately around 60,
larger values are often not achievable or come at the expense of a very poor
grating quality and performance.

@@

Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
$>\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source- and analyzer gratings ($>90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
approx. $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is limited by the grating size and the geometric
magnification of the sample, yielding a maximum field of view of
$\SI{30}{\milli\metre}$. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction. X-rays which are not travelling
through all of the gratings do not contribute to the signal and are
attenuated by the slits.

@@

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. This shows the
benefit of the phase nature of the image, which may be
useful to identify flaws in multilayered structures such as electronic
chips.
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

@@

\section*{Methods}
Edge-on illuminated gratings were manufactured by Micro
Works GmbH, Germany, using a LIGA process \cite{Kenntner2010}. Each grating
resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
is a symmetric Talbot-Lau interferometer with a grating period of $p =
\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
grating is positioned $\SI{23}{\centi\metre}$ away from the source. The
number of phase steps for one projection was 24 \cite{Weitkamp2005} and the
exposure time for the images was 15 seconds per phase step.

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
maximum voltage. The focal spot size is approximately
$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
\metre}$ thickness converts the X-rays to visible light and is coupled with
an optical lens projecting the image onto the CCD. The effective pixel size
is $\SI{80}{\micro \metre}$. The widths of the collimating slits are
$\SI{25}{\micro \metre}$ and $\SI{100}{\micro \metre}$, respectively.

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps
\cite{Weitkamp2005} and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). As the quality in the manufacturing of the
structure increases, the exposure time can become substantially shorter.

@@

\bibliographystyle{apsrev4-1}

@@

\begin{thebibliography}{25}%

@@

>>>>

%% ----------------------------------------------------------------------------------------------------------------
\begin{abstract}
    X-ray grating interferometry is a promising imaging technique sensitive
    to attenuation, refraction and scattering of the radiation. Applications
    of this technique in the energy range between $80$ and
    $\SI{150}{\kilo\electronvolt}$ are still largely unexplored due to the
    severe technical challenges. Phase-contrast X-ray imaging at such high
    energies is of relevant scientific and industrial interest, in
    particular for the investigation of materials with high atomic number or
    thickness as well as for medical imaging. Here we show the successful
    implementation of a Talbot-Lau interferometer operated at
    $\SI{100}{\kilo\electronvolt}$ using a conventional X-ray tube and a
    compact geometry, with a total length of $\SI{54}{\centi\metre}$. We
    present edge-on illumination of the gratings to overcome their current
    fabrication limits as well as curved structures, to match beam
    divergence and allow large field of views on a short and efficient
    setup.
\end{abstract}
\maketitle

@@

The attenuation and phase shift properties are described by the complex index of refraction
$n=1-\delta(\mathbf{r},\lambda) + i \beta(\mathbf{r},\lambda)$.
The imaginary part $\beta(\mathbf{r},\lambda)$ is related to the
attenuation per unit length (attenuation coefficient) by $\mu = 4 \pi
\beta(\mathbf{r},\lambda) / \lambda$ and the total attenuation by an object
of thickness $d$ can be described by the line integral $L_\mu = \int_0^d
\mu(\mathbf{r},\lambda) \d{} \mathbf{r}$. Similarly, the real part
$\delta(\mathbf{r},\lambda)$ determines the phase shift per unit length by
$\phi = 2 \pi \delta / \lambda$ and the total phase shift is $L_\phi =
\int_0^d \phi(\mathbf{r}) \d{} \mathbf{r}$.

@@

In the past, a lot of effort has been invested into the development of
techniques which are sensitive to the phase shift. Since most of the
available phase contrast techniques rely on interference and thus typically
on optical hardware (e.g. crystals, gratings), they vary a lot in terms of
sensitivity, practical applicability or achievable resolution. The vast
majority of the methods, including crystal analyzer based
\cite{Davis1995,Chapman1997} or interferometric \cite{Bonse1965,Momose1996}
methods rely on X-ray beams of high spatial and temporal coherence, which is
available only at synchrotron sources. Techniques which are compatible with
an X-ray beam of low temporal coherence (broad bandwidth) are the inline
phase contrast method \cite{Snigirev1995,Wilkins1996,Cloetens1996} and
Talbot interferometry \cite{Cloetens1997,David2002,Momose2003a}.
Phase-contrast imaging using X-ray beams of low temporal \emph{and}
spatial coherence such as conventional low-brilliance X-ray tubes have been
demonstrated with Talbot-Lau interferometry \cite{Pfeiffer2006} and coded
apertures \cite{Munro2012}.
In addition to phase sensitivity, these techniques provide a dark-field
contrast, also called scatter contrast or visibility-reduction contrast,
that is proportional to the scatter strength of details in the sample\cite{Pfeiffer2008}.

Talbot interferometry has been demonstrated using a synchrotron source at
$\SI{82}{\kilo\electronvolt}$\cite{Willner2013} and
$\SI{123}{\kilo\electronvolt}$\cite{Ruiz2013}.
Using a low-brilliance X-ray tube, Talbot-Lau interferometry was
applied at $\SI{60}{\kilo\electronvolt}$ mean energy \cite{Donath2009}.
Medical imaging applications may benefit from phase contrast at higher
energies: chest or abdominal
radiography or \ac{CT} require energies between $100$ and
$\SI{150}{\kilo\electronvolt}$. Other potential applications are homeland
security or chip failure analysis, which require high energies for the
visualization of materials of high density and atomic number.

Here, we introduce a method for phase-contrast imaging which is
compatible with the entire diagnostic energy range of X-rays. Moreover, the
method is fully compatible with compact imaging arrangements based on
conventional X-ray tubes. The method is based on Talbot-Lau interferometry
\cite{Pfeiffer2006} and employs an edge-on approach for the grating design and
arrangement. 
The challenge which limited the progress towards higher energies was mainly
related to the manufacturing of gratings with high aspect ratios. The aspect
ratio, given by
\begin{equation}
    \text{AR} = \frac{2h}{p},
\end{equation}
where $p$ is the grating period and $h$ the grating structure
height, is normally limited by the lithographic process, as grating
structures tend to collapse or to deform (e.g. through capillary forces) if
the aspect ratio is too high. For a given setup distance these parameters
depend on the target energy $E$ according to $p \propto
1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{AR}
\propto E^{7/2}$\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$ an aspect ratio
for the absorption grating of around $\textnormal{AR}=30$ is necessary for a
reasonable length of the experimental arrangement, it would have to be at
least $128$ for $E=\SI{100}{\kilo\electronvolt}$. Moreover, when using a
broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, which requires even higher aspect ratios.
Maximum achievable aspect ratios of current grating fabrication techniques
\cite{David2007,Kenntner2010} are approximately around 60,
larger values are often not achievable or come at the expense of a very poor
grating quality and performance.

@@

Due to the high spectral acceptance \cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source and analyzer gratings ($>90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a grating structure height of
approx. $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is limited by the grating size and the geometric
magnification of the sample, yielding a maximum field of view of
$\SI{30}{\milli\metre}$. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction. X-rays which are not travelling
through all of the gratings do not contribute to the signal and are
attenuated by the slits.

@@

Fig.~\ref{Fig:img_chip} shows a radiographic scan of an electronic chip.
Several resistors and an integrated circuits are located on different layers
on the chip. The images were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
digital differentiation. In the attenuation image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. This shows the
benefit of the phase nature of the image, which may be
useful to identify flaws in multilayered structures such as electronic
chips.
\begin{figure}[ht]
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}
    \label{Fig:img_chip}
\end{figure}

@@

\section*{Methods}
Edge-on illuminated gratings were manufactured by Microworks GmbH, Germany, using a LIGA process \cite{Kenntner2010}. Each grating
resides on a $5 \times \SI{60}{\milli\metre^2}$ silicon chip and several
grating chips are fabricated on a single 4 inch silicon wafer. The
experimental arrangement for a design energy at \SI{100}{\kilo\electronvolt}
is a symmetric Talbot-Lau interferometer with a grating period of $p =
\SI{2.8}{\micro \metre}$ for all gratings. The distance from the source
grating to the analyzer grating is $\SI{32}{\centi\metre}$ and the source
grating is positioned $\SI{23}{\centi\metre}$ away from the source.

The X-ray source is a COMET MXR-160HP/11 X-ray tube with a maximum output
voltage of $\SI{160}{\kilo\volt}$. In the experiment, it was set to the
maximum voltage. The focal spot size is approximately
$\SI{1}{\milli\metre}$. The detector is a CCD camera from Finger Lakes
Instruments. A cesium iodide (CsI:Ti) scintillator of $\SI{600}{\micro
\metre}$ thickness converts the X-rays to visible light and is coupled with
an optical lens projecting the image onto the CCD. The effective pixel size
is $\SI{80}{\micro \metre}$. The widths of the collimating slits are
$\SI{25}{\micro \metre}$ and $\SI{100}{\micro\metre}$, respectively.

In Fig.~\ref{Fig:img_chip}, image acquisition involved 24 phase steps per
line \cite{Weitkamp2005} and an exposure time of 15 seconds per step. The long
exposure times are mostly constrained by the low average visibility of the
gratings (\SI{5}{\percent}). The exposure time can be shortened with better
gratings and an efficient detector.

@@

\bibliographystyle{apsrev4-1}
 %\bibliography{library}

@@

\begin{thebibliography}{26}%

@@

\bibitem [{\citenamefont {Pfeiffer}\ \emph {et~al.}(2008)\citenamefont
  {Pfeiffer}, \citenamefont {Bech}, \citenamefont {Bunk}, \citenamefont
  {Kraft}, \citenamefont {Eikenberry}, \citenamefont {Br\"{o}nnimann},
  \citenamefont {Gr\"{u}nzweig},\ and\ \citenamefont {David}}]{Pfeiffer2008}%
  {Pfeiffer}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Bech}},
  \bibinfo {author} {\bibfnamefont {O.}~\bibnamefont {Bunk}}, \bibinfo {author}
  {\bibfnamefont {P.}~\bibnamefont {Kraft}}, \bibinfo {author} {\bibfnamefont
  {E.}~\bibnamefont {Eikenberry}}, \bibinfo {author} {\bibfnamefont
  {C.}~\bibnamefont {Br\"{o}nnimann}}, \bibinfo {author} {\bibfnamefont
  {C.}~\bibnamefont {Gr\"{u}nzweig}}, \ and\ \bibinfo {author} {\bibfnamefont
  {C.}~\bibnamefont {David}},\ }\href {\doibase 10.1038/nmat2096} {\bibfield
  {journal} {\bibinfo  {journal} {Nature Materials}\ }\textbf {\bibinfo
  {volume} {7}},\ \bibinfo {pages} {134} (\bibinfo {year} {2008})}\BibitemShut
